---
title: "p8105_hw1_hz2770"
author: "Hao Zheng"
date: "2021/9/28"
output: html_document
---

```{r}
library(tidyverse)
```

## Problem 1

This is a dataframe which contains four variables.

```{r}
example_df = tibble(
  norm_samp = rnorm(10),
  vec_logical = norm_samp > 0,
  vec_char = c("v","i","c","t","o","r","i","a","t","h"),
  vec_factor =c("low","medium","low","high","high","medium","low","high","medium","medium")
)
```

Then take the mean of each variable and see what will happen.

```{r}
x = pull(example_df,norm_samp)
mean(x)

y = pull(example_df,vec_logical)
mean(y)

z = pull(example_df,vec_char)
mean(z)

w = pull(example_df,vec_factor)
mean(w)
```

Oops! We can only take the mean of the numeric and logical value in the dataframe, why is that?

Let's try to apply as.numeric() fuction on all the variables.

```{r, eval=FALSE}
as.numeric(x)

as.numeric(y)

as.numeric(z)

as.numeric(w)
```

We can see from above that besides the numeric varible norm_samp, the logical variable can be view as the numerical values 0 or 1. Therefore, we only can take the mean of numeric and logical variables. Character and factor variables can not be viewed as numeric values, so we can't take their mean.


## Problem 2

First, download a package containing the penguins dataset in the console.
Then load this dataset.
```{r}
# load the penguins dataset
data("penguins", package = "palmerpenguins")
```
The dataset penguins contains 8 variables, among which, "species" and "island" are character variables; "bill_length_mm", "bill_depth_mm", "flipper_length_mm", "body_mass_g" and "year" are numeric variables; "sex" is factor variable.

For the size of this dataset, `nrow = 344`, and `ncol = 8`, mean flipper length is `r mean(pull(penguins, flipper_length_mm),na.rm = TRUE)`.
